### 2015-05-23 doc/thesis/glossary.tex
Some improvements to glossary

\item[closed table type] It is a table type that does not allow adding fields.

@@

\item[consistency] It is a relation that gradual typing uses to control the insertion of
run-time checks between dynamically typed and statically typed code.

\item[consistent-subtyping] It is a relation that combines consistency and subtyping.

\item[contravariant] Subtyping is contravariant when it reverses the subtyping order,
that is, it orders types from a more generic type to a more specific type.

\item[covariant] Subtyping is covariant when it preserves the subtyping order,
that is, it orders types from a more specific type to a more general type.

\item[depth subtyping] It allows changing the type of individual fields of a table type.

@@

\item[filter type] It is a type that allows Typed Lua to discriminate the type of local variables
inside control flow statements.

\item[fixed table type] It is a table type that does not allow adding fields. It also does not allow
width subtyping to make single inheritance safe.

\item[flow typing] It is a combination of static typing and flow analysis.

@@

\item[gradual type system] It is a type system that uses the consistency relation to check the interaction
among the dynamic type and other types.

\item[gradual typing] It is an approach that uses a gradual type system to allow static and dynamic
typing in the same code, but inserting run-time checks between statistically
typed and dynamically typed code.

\item[invariant] Subtyping is invariant when it does not allow ordering types, that is,
it is a way that express type equality through subtyping.

\item[metatable] It is a Lua table that allows changing its behavior.

\item[nominal type system] It is a type system that uses name declarations to define the equivalence among types.

\item[open table type] It is a table type that allows adding fields, and usually refers to table types that
have aliases.

@@

\item[projection environment] It is a type environment that Typed Lua uses to assign projection variables to
second-level types.

\item[projection type] It is a type that allows Typed Lua to discriminate the type of local variables
that have a dependency relation.

\item[prototype object] It is an object that works like a class, that is, it is a prototype for creating
new objects of a given class.

\item[self-like delegation] It is a technique to implement inheritance in dynamically typed languages.

@@

\item[structural type system] It is a type system that uses the type structure to define the equivalence among types.

@@

\item[type environment] It is an environment that assigns variable names to types.

@@

\item[unique table type] It is a table type that allows adding fields, and it is also the table type
that describe the type of the table constructor.

@@

\item[userdata] It is a way to define new types in an application or library that is written in C.

@@

\item[width subtyping] It allows adding more fields to a table type.

>>>>

\item[closed table type] It is the type of table annotations in Typed Lua.
A closed table type does not provide any guarantees that about keys
with types not listed in the table type, and it also does not
allow adding fields to the table type.

@@

\item[consistency] Gradual typing uses the consistency relation instead of type equality
to check the interaction among the dynamic type and other types.
This relation allows us combining dynamic and static typing in the
same language, but still catching static type errors.
The consistency relation is reflexive and symmetric, but it is not transitive.

\item[consistent-subtyping] It is a relation that combines consistency and subtyping, allowing
the definition of gradual type systems for object-oriented languages.
The consistent-subtyping relation is reflexive and symmetric, but it is not transitive.

\item[contravariant] Subtyping is contravariant when it reverses the subtyping order,
that is, a subtyping rule is contravariant when it orders
types from more generic types (supertypes) to more specific types (subtypes).

\item[covariant] Subtyping is covariant when it preserves the subtyping order,
that is, a subtyping rule is covariant when it orders
types from more specific types (subtypes) to more general types (supertypes).

\item[depth subtyping] It allows the supertype to change the type of individual fields in the subtype.

@@

\item[filter type] It is a type that allows Typed Lua to discriminate and restore the type of
local variables inside control flow statements.

\item[fixed table type] It is a table type that does not allow width subtyping to make single
inheritance safe in Typed Lua, and it also does not allow adding fields to
the table type.

\item[flow typing] It is a combination of static typing and flow analysis to allow variables
to have different types at different parts of the program.

@@

\item[gradual type system] It is a type system that uses the consistency relation instead of type equality
to check the interaction among the dynamic type and other types.

\item[gradual typing] It is an approach that uses a gradual type system to allow static and dynamic
typing in the same code, but inserting run-time checks between statistically
typed and dynamically typed code.
This run-time checks ensure that dynamically typed code does not violate
statically typed code.

\item[invariant] Subtyping is invariant when it does not allow ordering types, that is,
it is a way to define type equality through subtyping.

\item[metatable] It is a Lua table that allows changing the behavior of other tables
it is attached to.

\item[nominal type system] It is a type system that uses the name of the types to check the
compatibility among them.

\item[open table type] It is the type of the tables with keys that do not inhabit one of
the table's key types, have at least one alias, and allows adding
fields to the table type.

@@

\item[projection environment] It is an environment that Typed Lua uses to assign projection variables to
second-level types.

\item[projection type] It is a type that allows Typed Lua to discriminate the type of local variables
that have a dependency relation, as they include a projection variable and an
index that allow Typed Lua to project unions of second-level types into
unions of first-level types.

\item[prototype object] It is an object that works like a class, that is, it is an object from
which other objects inherit its attributes.

\item[self-like delegation] It is a technique to implement inheritance in dynamically typed languages
through prototype objects.

@@

\item[structural type system] It is a type system that uses the structure of types to check the compatibility among them.

@@

\item[type environment] It is an environment that Typed Lua uses to assign variable names to first-level types.

@@

\item[unique table type] It is the type of the tables with keys that do not inhabit one of
the table's key types, does not have any alias, and allow adding
fields to the table type.
It is also the table type that describes the type of the table constructor.

@@

\item[userdata] It is a Lua data type that allows Lua variables to hold values from applications
or libraries that are written in C.

@@

\item[width subtyping] It allows the subtype to have fields that do not exist in the supertype.
